Hemispheric Lateralization and Outcomes After ICH: A Pooled Analysis of Clinical Trials

### 2022-09-22 study protocol.qmd
Combined ATACH and ERICH

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tableone)
library(data.table)
```

### Pooling RCTs

Randomized trials and observational studies included in the analysis:

-   ATACH2
-   ERICH
-   MISTIE
-   MISTIE III
-   CLEAR-IVH

```{r setup, include=FALSE}

# ATACH2

@@

atachmrs30 <- atach09 %>%
  filter(mrsday == 30) %>%
  select(SUBJECT_ID, F09Q01) %>%
  rename(mrs30 = F09Q01)

atachmrs90 <- atach09 %>%
  filter(mrsday == 90) %>%
  select(SUBJECT_ID, F09Q01) %>%
  rename(mrs90 = F09Q01)

@@

@@

atachVarsTableOne <- c("F33O02", "F01Q01", "F01Q02", "F01Q03M1", "F01Q03M2", "F01Q03M3", "F01Q03M5", "F01Q03M6", "F01Q03M7", "SITE_ID", "COUNTRY", "F03Q01", "F03Q04", "F03Q05", "F03Q06", "F03Q07", "F03Q09", "F03Q12", "F03Q13", "F04Q01", "F04Q03", "F00Q02MIN", "F05Q07a", "F05Q07b", "F33Q04", "F10Q22", "F15Q11", "F15Q04", "F15Q07", "F15Q09", "F15Q12", "F15Q17", "CTCRQ05", "CTCRQ07
", "CTCRQ08", "CTCRQ12", "CTCRQ13", "CTCRQ11", "CTCRQ14", "F07Q01", "F07Q02", "F07Q11", "F07Q04DAY", "F07Q05", "F07Q07", "F07Q08", "F07Q09DAY")

@@

Variables included:

-   Age

-   Gender

-   Country Randomized

-   RCT enrolled in

-   Intracerebral hemorrhage

-   Ischemic stroke

-   Coronary artery disease

-   Congestive heart failure

-   Chronic kidney disease

-   Obesity

-   Hypertension

-   Diabetes

-   Antihypertensive therapy

-   Anticoagluation therapy

-   Antiplatelet therapy

-   Lipid lowering therapy

-   Time from onset to presentation

-   Systolic BP

-   Diastolic BP

-   Median GCS

-   Median NIHSS

-   Glucose

-   Hematoma volume

-   Hematoma location

-   IVH

-   ICH Score

-   Extraventricular drain

-   Craniotomy

-   WLST

-   Median time to WLST

-   mRS

-   EuroQOL

-   BI

-   Living at home

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tableone)
library(data.table)
library(haven) # Importing SAS Files

```{r ATACH2, include=FALSE}

@@

atachmrs30 <- atach09 %>%
  filter(mrsday == 30) %>%
  select(SUBJECT_ID, F09Q01) %>%
  rename(mrs.30 = F09Q01)

atachmrs90 <- atach09 %>%
  filter(mrsday == 90) %>%
  select(SUBJECT_ID, F09Q01) %>%
  rename(mrs.90 = F09Q01)

@@

# Categorizing and Recoding Variables

# Race
atach.whole <- atach.whole %>%
  mutate(race = case_when(
    F01Q03M1 == 1 ~ "American Indian or Alaskan Native",
    F01Q03M2 == 1 ~ "Asian",
    F01Q03M3 == 1 ~ "Black or African-American",
    F01Q03M5 == 1 ~ "White",
    F01Q03M6 == 1 ~ "Other/Not Reported",
    F01Q03M7 == 1 ~ "Other/Not Reported"
  ))

# Ethnicity
atach.whole <- atach.whole %>% 
  mutate(ethnicity = recode(F01Q02,
                             "1" = "Hispanic or Latino",
                             "2" = "Not Hispanic or Latino",
                             .default = "Unknown/Not Reported"
                             ))

# Sex
atach.whole <- atach.whole %>% 
  mutate(sex = dplyr::recode(F01Q01,
                      "1" = "Male",
                      "2" = "Female"))

# Country of Enrolling Site
atach.whole <- atach.whole %>% 
  mutate(enrolling.country = recode(COUNTRY,
                                    "1" = "United States",
                                    "2" = "Japan",
                                    "3" = "China",
                                    "4" = "South Korea",
                                    "5" = "Taiwan",
                                    "6" = "Germany"))

# Past Medical History
atach.whole <- atach.whole %>%
  mutate(stroke = recode(F03Q01,
                         "0" = "No",
                         "1" = "Yes",
                         "98" = "NA"))

atach.whole <- atach.whole %>%
  mutate(chf = recode(F03Q03,
                         "0" = "No",
                         "1" = "Yes",
                         "98" = "NA"))

atach.whole <- atach.whole %>%
  mutate(afib = recode(F03Q04,
                         "0" = "No",
                         "1" = "Yes",
                         "98" = "NA"))

atach.whole <- atach.whole %>%
  mutate(cad = case_when(
    F03Q05 == 0 ~ "No",
    F03Q05 == 1 ~ "Yes",
    F03Q05 == 98 ~ "NA",
    F03Q06 == 0 ~ "No",
    F03Q06 == 1 ~ "Yes",
    F03Q06 == 98 ~ "NA"
  ))

atach.whole <- atach.whole %>%
  mutate(htn = recode(F03Q07,
                         "0" = "No",
                         "1" = "Yes",
                         "98" = "NA"))

atach.whole <- atach.whole %>%
  mutate(pvd = recode(F03Q08,
                         "0" = "No",
                         "1" = "Yes",
                         "98" = "NA"))

atach.whole <- atach.whole %>%
  mutate(hld = recode(F03Q09,
                         "0" = "No",
                         "1" = "Yes",
                         "98" = "NA"))

atach.whole <- atach.whole %>%
  mutate(dm2 = recode(F03Q12,
                         "0" = "No",
                         "1" = "Yes",
                         "98" = "NA"))

atach.whole <- atach.whole %>%
  mutate(tobacco = recode(F03Q13,
                         "0" = "No",
                         "1" = "Yes",
                         "98" = "NA"))

# ICH Laterality
atach.whole <- atach.whole %>%
  mutate(ich.laterality = recode(ich.location.baseline,
                                 "1" = "Right",
                                 "2" = "Right",
                                 "3" = "Right",
                                 "4" = "Left",
                                 "5" = "Left",
                                 "6" = "Left",
                                 .default = "NA"))

# ICH Location
atach.whole <- atach.whole %>%
  mutate(ich.location.baseline = recode(ich.location.baseline,
                                        "1" = "Thalamus",
                                        "2" = "Basal Ganglia",
                                        "3" = "Lobar",
                                        "4" = "Thalamus",
                                        "5" = "Basal Ganglia",
                                        "6" = "Lobar",
                                        "7" = "Pons",
                                        "8" = "Cerebellum"))

atach.whole <- atach.whole %>%
  mutate(ivh = recode(ivh.baseline,
                         "0" = "No",
                         "1" = "Yes",
                         "98" = "NA"))

atach.whole <- atach.whole %>%
  mutate(hydrocephalus = recode(hydrocephalus.baseline,
                         "0" = "No",
                         "1" = "Yes",
                         "98" = "NA"))

atach.whole <- atach.whole %>%
  mutate(hydrocephalus = recode(hydrocephalus.baseline,
                         "0" = "No",
                         "1" = "Yes",
                         "98" = "NA"))

atach.whole <- atach.whole %>%
  mutate(ich.volume.cc = ich.volume.baseline/1000)

atach.whole <- atach.whole %>%
  mutate(phe.volume.cc = phe.volume.baseline/1000)

atach.whole <- atach.whole %>%
  mutate(ivh.volume.cc = ivh.volume.baseline/1000)

atach.whole <- atach.whole %>%
  mutate(mech.ventilation = recode(F07Q01,
                                   "0" = "No",
                                   "1" = "Yes",
                                   .default = "NA"))

atach.whole <- atach.whole %>%
  mutate(evd = recode(F07Q05,
                                   "0" = "No",
                                   "1" = "Yes",
                                   .default = "NA"))

atach.whole <- atach.whole %>%
  mutate(nsgy.evacuation = recode(F07Q08,
                                   "0" = "No",
                                   "1" = "Yes",
                                   .default = "NA"))

atach.whole <- atach.whole %>%
  mutate(trach = recode(F07Q11,
                                   "0" = "No",
                                   "1" = "Yes",
                                   .default = "NA"))

# NIHSS
atach.nihss.baseline <- atach10 %>%
  filter(nihss.assessment == "baseline") %>%
  select(SUBJECT_ID, F10Q22) %>%
  rename(nihss.baseline = F10Q22)

atach.nihss.24hourpost <- atach10 %>%
  filter(nihss.assessment == "24hourpost") %>%
  select(SUBJECT_ID, F10Q22) %>%
  rename(nihss.24hourpost = F10Q22)

atach.whole <-left_join(atach.whole, atach.nihss.baseline, by = "SUBJECT_ID")
atach.whole <-left_join(atach.whole, atach.nihss.24hourpost, by = "SUBJECT_ID")

# EuroQol

atach.whole <- atach.whole %>%
  mutate(euro.mobility.90 = factor(F16Q02,
                                labels = c("No Problems", "Some Problems", "Confined to Bed")))

atach.whole <- atach.whole %>%
  mutate(euro.selfcare.90 = factor(F16Q03,
                                labels = c("No Problems", "Some Problems", "Unable to Wash or Dress Myself")))

atach.whole <- atach.whole %>%
  mutate(euro.usual.90 = factor(F16Q04,
                                labels = c("No Problems", "Some Problems", "Unable to Perform My Usual Activities")))

atach.whole <- atach.whole %>%
  mutate(euro.pain.90 = factor(F16Q05,
                                labels = c("No Pain/Discomfort", "Some Moderate Pain/Discomfort", "Extreme Pain/Discomfort")))

atach.whole <- atach.whole %>%
  mutate(euro.anxiety.90 = factor(F16Q06,
                                labels = c("Not Anxious/Depressed", "Moderately Anxious/Depressed", "Extremely Anxious/Depressed")))

# Filtering out cases without ICH laterality
atach.whole <- atach.whole %>%
  filter(ich.laterality != "NA")

@@

atach.whole <- atach.whole %>%
  rename(age = F33Q02) %>%
  rename(symptom.onset = F00Q02MIN) %>%
  rename(sbp.initial = F05Q07A) %>%
  rename(dbp.initial = F05Q07B) %>%
  rename(gcs.baseline = F33Q04) %>%
  rename(intubation.days = F07Q02) %>%
  rename(extubation.date = F07Q03DAY) %>%
  rename(trach.date = F07Q04DAY) %>%
  rename(evd.days = F07Q07) %>%
  rename(nsgy.evacuation.date = F07Q09DAY) %>%
  rename(euro.vas.90 = F16Q07) %>%
  rename(EQ_INDEX.90 = EQ_INDEX)

VarsTableOne <- c("study",
                  "age", # Age
                       "sex", # Sex
                       "ethnicity", # Ethnicity
                       "race", # Race
                       "enrolling.country", # Country of Enrolling Site
                       "stroke", 
                       "cad", 
                       "chf", 
                       "afib", 
                       "pvd",
                       "hld",
                       "dm2",
                       "tobacco",
                       #"symptom.onset", # Time of symptom onset
                       "sbp.initial", # Initial SBP
                       "dbp.initial", # Initial DBP
                       "gcs.baseline", # Baseline GCS
                       #"nihss.baseline", # NIHSS
                       "ich.location.baseline", 
                       "ivh",
                      # "hydrocephalus",
                       "ich.volume.cc",
                       "ivh.volume.cc",
                       "phe.volume.cc",
                       "sp.shift.baseline",
                       "mech.ventilation",
                       "intubation.days", 
                       "extubation.date", # Date of extubation
                       "trach",
                       "trach.date", # Date of Tracheostomy
                       "evd",
                       "evd.days", # Total EVD days
                       "nsgy.evacuation",
                       "nsgy.evacuation.date",  # Date of Evacuation
                       "mrs.30",
                       "mrs.90",
                      "mrs.180",
                      "mrs.365",
                      "euro.mobility.90",
                      "euro.mobility.180",
                      "euro.mobility.365",
                       "euro.selfcare.90",
                      "euro.selfcare.180",
                      "euro.selfcare.365",
                       "euro.usual.90",
                      "euro.usual.180",
                      "euro.usual.365",
                       "euro.pain.90",
                      "euro.pain.180",
                      "euro.pain.365",
                       "euro.anxiety.90",
                      "euro.anxiety.180",
                      "euro.anxiety.365",
                       "euro.vas.90", # EuroQOL VAS
                       "euro.vas.180",
                       "euro.vas.365",
                       "EQ_INDEX.90", # EQ-5D Utility Index,,
                      "current.location.90",
                      "current.location.180",
                      "current.location.365",
                       "ich.laterality"
                  )

# Maybe import lab data, but this may be superfluous

@@

## Table 1 ATACH-2

```{r ATACH table1, echo=FALSE}

atach.table1.data <- atach.whole %>%
  select(atachVarsTableOne)

CreateTableOne(vars = atachVarsTableOne,
               data = atach.whole,
               strata = "ich.laterality")

```{r ERICH, include=FALSE}

erich.case <- read_sas("ERICH/erich_case_100217.sas7bdat")

erich.whole <- erich.case %>%
  select(ID, age, gender, Race, Ethnicity, D6, D7, D7A, D21, D21A, D22, D25, PHY4, PHY6, PHY6A, PHY9, 1510, 1511, 1512, ED7, ED8, ED36, ED37, ED38, ED39, ED44, ED47_SYS, ED47_DIAS, SH1, SH8, SH9, SH10, SMK1A, MHX1, MHX3, MHX3A, MHX6, MHX8, MHX9, MHX11, MHX12, MHX13, MHX13A, MHX14, MHX16, MHX18, MHX20, MHX21, MHX22, MHX27C, MHX28, SA1, SA4, SA5A, SA6, SE1, SE2, SE3, SE15, LAB5, LAB6, IT5D, detail, ICH_Loc_CT1, ICH_Vol_CT1, IVH_Vol_CT1, ICH_Vol_CT2, ICH_Vol_CT3, ICH_Vol_CT4, IVH_Present, IT5D_DATE, IT5D_TIME, IT5H, IT5H_DATE, IT5H_TIME, IT5I, IT5I_DATE, IT5I_TIME, IT5F, IT5F_SPEC, IT5F_DATE, IT5F_TIME, IT7, IT8, IT8A, IT8B, IT13, IT13A, IT24, IT24A_DATE, IT24A_TIME, IT24A_UNITS, IT29, IT29A, IT29B, IT21, IT22, IT25, IT23, IT28, CC16, CC16_DATE, CC16_TIME, CC17, CC17_DATE, CC17_TIME, CC18, CC18_DATE, CC18_TIME, CX15, CX27, CX30, O3, O3A, O5, O20, AU8, AU8_OTH, RANKIN_FU1, RANKIN_FU2, RANKIN_FU3, MOBILITY_FU1, MOBILITY_FU2, MOBILITY_FU3, SELFCARE_FU1, SELFCARE_FU2, SELFCARE_FU3, USUALACT_FU1, USUALACT_FU2, USUALACT_FU3, PAIN_FU1, PAIN_FU2, PAIN_FU3, ANXIETY_FU1, ANXIETY_FU2, ANXIETY_FU3, HLTHSTAT_FU1, HLTHSTAT_FU2, HLTHSTAT_FU3, FEED_FU1, FEED_FU2, FEED_FU3, BATHE_FU1, BATHE_FU2, BATHE_FU3, GROOM_FU1, GROOM_FU2, GROOM_FU3, DRESS_FU1, DRESS_FU2, DRESS_FU3, BOWELS_FU1, BOWELS_FU2, BOWELS_FU3, BLADDER_FU1, BLADDER_FU2, BLADDER_FU3, TOILET_FU1, TOILET_FU2, TOILET_FU3, TRANSFER_FU1, TRANSFER_FU2, TRANSFER_FU3, MOBLEVEL_FU1, MOBLEVEL_FU2, MOBLEVEL_FU3, STAIRS_FU1, STAIRS_FU2, STAIRS_FU3, BART_TOT_FU1, BART_TOT_FU2, BART_TOT_FU3, EMS33, ED44, CURR_LOC_FU1, CURR_LOC_FU2, CURR_LOC_FU3)

erich.whole <- erich.whole %>%
  mutate(study = "ERICH")

erich.whole <- erich.whole %>%
  mutate(enrolling.country = "United States")

# Renaming and Recoding Variables

erich.whole <- erich.whole %>%
  mutate(gender = recode(gender,
                         "F" = "Female",
                         "M" = "Male")) %>%
  rename(sex = gender)

erich.whole <- erich.whole %>%
  mutate(Race = case_when(
    D21 == "W" ~ "White",
    D21 == "B" ~ "Black or African-American",
    D21 == "A" ~ "Asian",
    D21 == "N" ~ "Native Hawaiian/Pacific Islander",
    D21 == "I" ~ "American Indian or Alaskan Native",
    D21 == "O" ~ "Other/Not Reported",
    D21 == "U" ~ "Other/Not Reported"
    )) %>%
  rename(race = Race)

erich.whole <- erich.whole %>%
  mutate(Ethnicity = case_when(
    D21A == "H" ~ "Hispanic or Latino",
    D21A == "N" ~ "Not Hispanic or Latino",
    D21A == "U" ~ "Not Hispanic or Latino"
  ))

erich.whole <- erich.whole %>%
  mutate(stroke = recode(SH1,
                         "2" = "No",
                         "1" = "Yes",
                         "8" = "NA"))

erich.whole <- erich.whole %>%
  mutate(cad = recode(MHX8,
                         "2" = "No",
                         "1" = "Yes",
                         "8" = "NA"))

erich.whole <- erich.whole %>%
  mutate(chf = recode(MHX13,
                         "2" = "No",
                         "1" = "Yes",
                         "8" = "NA"))

erich.whole <- erich.whole %>%
  mutate(afib = recode(MHX11,
                         "2" = "No",
                         "1" = "Yes",
                         "8" = "NA"))

erich.whole <- erich.whole %>%
  mutate(pvd = recode(MHX27C,
                         "2" = "No",
                         "1" = "Yes",
                         "8" = "NA"))

erich.whole <- erich.whole %>%
  mutate(hld = recode(MHX6,
                         "2" = "No",
                         "1" = "Yes",
                         "8" = "NA"))

erich.whole <- erich.whole %>%
  mutate(dm2 = case_when(
    MHX3 == "2" ~ "No",
    MHX3 == "8" ~ "NA",
    MHX3A == "1" ~ "No",
    MHX3A == "2" ~ "Yes",
    MHX3A == "8" ~ "NA"))

erich.whole <- erich.whole %>%
  mutate(tobacco = recode(SMK1A,
                         "2" = "No",
                         "1" = "Yes",
                         "5" = "NA",
                         "8" = "NA"))

erich.whole <- erich.whole %>%
  rename(sbp.initial = ED47_SYS)

erich.whole <- erich.whole %>%
  rename(dbp.initial = ED47_DIAS)

erich.whole <- erich.whole %>%
  rename(gcs.baseline = ED39)

erich.whole <- erich.whole %>%
  mutate(ich.laterality = recode(PHY6A,
                                 "L" = "Left",
                                 "R" = "Right",
                                 "M" = "NA",
                                 .default = "NA"))

erich.whole <- erich.whole %>%
  mutate(ich.location.baseline = recode(erich.case$detail,
                                        "L Thalamic" = "Thalamus",
                                        "R Thalamic" = "Thalamus",
                                        "L Caudate Nucleus" = "Basal Ganglia",
                                        "L Cerebellar" = "Cerebellum",
                                        "L Corona Radiata" = "Lobar",
                                        "L Frontal" = "Lobar",
                                        "L Frontal Temporal" = "Lobar",
                                        "L Frontoparietal" = "Lobar",
                                        "L Occipital" = "Lobar",
                                        "L Parietal" = "Lobar",
                                        "L Parieto-Occipital" = "Lobar",
                                        "L Periventricular" = "Basal Ganglia",
                                        "L Putaminal" = "Basal Ganglia",
                                        "L Temporal" = "Lobar",
                                        "L Temporal-Parietal-Occipital (L Hemisphere)" = "Lobar",
                                        "L Temporal Occipital" = "Lobar",
                                        "L Temporal parietal" = "Lobar",
                                        "Multiple Hemorrhages - Deep" = "Basal Ganglia",
                                        "Multiple Hemorrhages - Lobar" = "Lobar",
                                        "Not applicable" = "NA",
                                        "Primary IVH" = "Primary IVH",
                                        "R Basal Ganglia" = "Basal Ganglia",
                                        "R Caudate Nucleus" = "Basal Ganglia",
                                        "R Cerebellar" = "Cerebellum",
                                        "R Frontal" = "Lobar",
                                        "R Frontal Temporal" = "Lobar",
                                        "R Frontoparietal" = "Lobar",
                                        "R Occipital" = "Lobar",
                                        "R Parietal" = "Lobar",
                                        "R Parieto-Occipital" = "Lobar",
                                        "R Periventricular" = "Basal Ganglia",
                                        "R Putaminal" = "Basal Ganglia",
                                        "R Temporal" = "Lobar",
                                        "R Temporal-Parietal-Occipital (R Hemisphere)" = "Lobar",
                                        "R Temporal Occipital" = "Lobar",
                                        "R Temporal Perietal" = "Lobar",
                                        "Unknown" = "NA",
                                        "Brainstem" = "Brainstem",
                                        "Cerebellar" = "Cerebellum",
                                        "R Temporal parietal" = "Lobar",
                                        "L Basal Ganglia" = "Basal Ganglia",                                        ))

erich.whole <- erich.whole %>%
  mutate(ivh = case_when(erich.case$IVH_Vol_CT1 > 0 ~ "Yes",
                         erich.case$IVH_Vol_CT1 < 0.1 ~ "No"))

erich.whole <- erich.whole %>%
  rename(ich.volume.cc = ICH_Vol_CT1)

erich.whole <- erich.whole %>%
  rename(ivh.volume.cc = IVH_Vol_CT1)

erich.whole <- erich.whole %>%
  mutate(mech.ventilation = case_when(
    EMS33 == "1" ~ "Yes",
    EMS33 == "2" ~ "No",
    ED44 == "1" ~ "Yes",
    ED44 == "2" ~ "No",
    IT7 == "1" ~ "Yes",
    IT7 == "2" ~ "No"))

erich.whole <- erich.whole %>%
  mutate(evd = case_when(
    IT8 == "1" ~ "Yes",
    IT8 == "2" ~ "No",
  ))

erich.whole <- erich.whole %>%
  mutate(nsgy.evacuation = case_when(
    IT5D == "1" ~ "Yes",
    IT5D == "2" ~ "No",
    IT5H == "1" ~ "Yes",
    IT5H == "2" ~ "No"
  ))

erich.whole <- erich.whole %>%
  rename(mrs.90 = RANKIN_FU1) %>%
  rename(mrs.180 = RANKIN_FU2) %>%
  rename(mrs.365 = RANKIN_FU3) %>%
  rename(euro.vas.90 = HLTHSTAT_FU1) %>%
  rename(euro.vas.180 = HLTHSTAT_FU2) %>%
  rename(euro.vas.365 = HLTHSTAT_FU3) %>%
  rename(barthel.feeding.90 = FEED_FU1) %>%
  rename(barthel.bathing.90 = BATHE_FU1) %>%
  rename(barthel.grooming.90 = GROOM_FU1) %>%
  rename(barthel.dressing.90 = DRESS_FU1) %>%
  rename(barthel.bowels.90 = BOWELS_FU1) %>%
  rename(barthel.bladder.90 = BLADDER_FU1) %>%
  rename(barthel.toilet.90 = TOILET_FU1) %>%
  rename(barthel.transfer.90 = TRANSFER_FU1) %>%
  rename(barthel.mobility.90 = MOBLEVEL_FU1) %>%
  rename(barthel.stairs.90 = STAIRS_FU1) %>%
  rename(barthel.total.90 = BART_TOT_FU1) %>%
  rename(barthel.feeding.180 = FEED_FU2) %>%
  rename(barthel.bathing.180 = BATHE_FU2) %>%
  rename(barthel.grooming.180 = GROOM_FU2) %>%
  rename(barthel.dressing.180 = DRESS_FU2) %>%
  rename(barthel.bowels.180 = BOWELS_FU2) %>%
  rename(barthel.bladder.180 = BLADDER_FU2) %>%
  rename(barthel.toilet.180 = TOILET_FU2) %>%
  rename(barthel.transfer.180 = TRANSFER_FU2) %>%
  rename(barthel.mobility.180 = MOBLEVEL_FU2) %>%
  rename(barthel.stairs.180 = STAIRS_FU2) %>%
  rename(barthel.total.180 = BART_TOT_FU2) %>%
  rename(barthel.feeding.365 = FEED_FU3) %>%
  rename(barthel.bathing.365 = BATHE_FU3) %>%
  rename(barthel.grooming.365 = GROOM_FU3) %>%
  rename(barthel.dressing.365 = DRESS_FU3) %>%
  rename(barthel.bowels.365 = BOWELS_FU3) %>%
  rename(barthel.bladder.365 = BLADDER_FU3) %>%
  rename(barthel.toilet.365 = TOILET_FU3) %>%
  rename(barthel.transfer.365 = TRANSFER_FU3) %>%
  rename(barthel.mobility.365 = MOBLEVEL_FU3) %>%
  rename(barthel.stairs.365 = STAIRS_FU3) %>%
  rename(barthel.total.365 = BART_TOT_FU3)

erich.whole <- erich.whole %>%
  mutate(current.location.90 = recode(CURR_LOC_FU1,
                      "1" = "Home",
                      "2" = "Rehabilitation",
                      "3" = "Skilled Nursing Facility",
                      "4" = "Hospital",
                      "7" = "Other"
                      )) %>%
  mutate(current.location.180 = recode(CURR_LOC_FU1,
                      "1" = "Home",
                      "2" = "Rehabilitation",
                      "3" = "Skilled Nursing Facility",
                      "4" = "Hospital",
                      "7" = "Other"
                      )) %>%
  mutate(current.location.365 = recode(CURR_LOC_FU1,
                      "1" = "Home",
                      "2" = "Rehabilitation",
                      "3" = "Skilled Nursing Facility",
                      "4" = "Hospital",
                      "7" = "Other"
                      ))

erich.whole <- erich.whole %>%
  mutate(euro.mobility.90 = factor(MOBILITY_FU1,
                                labels = c("No Problems", "Some Problems", "Confined to Bed", "NA")))

erich.whole <- erich.whole %>%
  mutate(euro.selfcare.90 = factor(SELFCARE_FU1,
                                labels = c("No Problems", "Some Problems", "Unable to Wash or Dress Myself", "NA")))

erich.whole <- erich.whole %>%
  mutate(euro.usual.90 = factor(USUALACT_FU1,
                                labels = c("No Problems", "Some Problems", "Unable to Perform My Usual Activities", "NA")))

erich.whole <- erich.whole %>%
  mutate(euro.pain.90 = factor(PAIN_FU1,
                                labels = c("No Pain/Discomfort", "Some Moderate Pain/Discomfort", "Extreme Pain/Discomfort", "NA")))

erich.whole <- erich.whole %>%
  mutate(euro.anxiety.90 = factor(ANXIETY_FU1,
                                labels = c("Not Anxious/Depressed", "Moderately Anxious/Depressed", "Extremely Anxious/Depressed", "NA")))

erich.whole <- erich.whole %>%
  mutate(euro.mobility.180 = factor(MOBILITY_FU2,
                                labels = c("No Problems", "Some Problems", "Confined to Bed")))

erich.whole <- erich.whole %>%
  mutate(euro.selfcare.180 = factor(SELFCARE_FU2,
                                labels = c("No Problems", "Some Problems", "Unable to Wash or Dress Myself")))

erich.whole <- erich.whole %>%
  mutate(euro.usual.180 = factor(USUALACT_FU2,
                                labels = c("No Problems", "Some Problems", "Unable to Perform My Usual Activities")))

erich.whole <- erich.whole %>%
  mutate(euro.pain.180 = factor(PAIN_FU2,
                                labels = c("No Pain/Discomfort", "Some Moderate Pain/Discomfort", "Extreme Pain/Discomfort")))

erich.whole <- erich.whole %>%
  mutate(euro.anxiety.180 = factor(ANXIETY_FU2,
                                labels = c("Not Anxious/Depressed", "Moderately Anxious/Depressed", "Extremely Anxious/Depressed")))

erich.whole <- erich.whole %>%
  mutate(euro.mobility.365 = factor(MOBILITY_FU3,
                                labels = c("No Problems", "Some Problems", "Confined to Bed")))

erich.whole <- erich.whole %>%
  mutate(euro.selfcare.365 = factor(SELFCARE_FU3,
                                labels = c("No Problems", "Some Problems", "Unable to Wash or Dress Myself")))

erich.whole <- erich.whole %>%
  mutate(euro.usual.365 = factor(USUALACT_FU3,
                                labels = c("No Problems", "Some Problems", "Unable to Perform My Usual Activities")))

erich.whole <- erich.whole %>%
  mutate(euro.pain.365 = factor(PAIN_FU3,
                                labels = c("No Pain/Discomfort", "Some Moderate Pain/Discomfort", "Extreme Pain/Discomfort")))

erich.whole <- erich.whole %>%
  mutate(euro.anxiety.365 = factor(ANXIETY_FU3,
                                labels = c("Not Anxious/Depressed", "Moderately Anxious/Depressed", "Extremely Anxious/Depressed")))

# Variables left: symptom.onset

# Variables missing: nihss.baseline, hydrocephalus, phe.volume.cc, sp.shift.baseline, intubation.days, tracheostomy, nsgy.evacuation.date,

# Filtering out ICH Laterality and Infratentorial Location
erich.whole <- erich.whole %>%
  filter(ich.laterality != "NA") %>%
  filter(ich.location.baseline == "Basal Ganglia" |
           ich.location.baseline == "Thalamus" |
           ich.location.baseline == "Lobar")

```{r combining ATACH2 and ERICH, include=FALSE}

atach.erich <- union_all(atach.whole, erich.whole)

atach.erich <- atach.erich %>%
  select(VarsTableOne) %>%
  mutate(ich.score.age = case_when(
    age < 80 ~ 0,
    age >= 80 ~ 1
  )) %>%
  mutate(ich.score.gcs = case_when(
    gcs.baseline >= 13 ~ 0,
    gcs.baseline <= 4 ~ 2,
    TRUE ~ 1)) %>%
  mutate(ich.score.volume = if_else(ich.volume.cc >= 30,1,0)) %>%
  mutate(ich.score.ivh = if_else(ivh == "Yes",1,0)) %>%
  mutate(ich.score.total = ich.score.age + 
                           ich.score.gcs + 
                           ich.score.volume +
                           ich.score.ivh)
